---
title: "data_clean"
author: "Kendy Teng"
date: "2/20/2020"
output: html_document
---

```{r setup, include=FALSE}
source("G:/Mi unidad/Statistics/R-stats/R function/my functions/functions/script/data_clean.R")
```

## Intro
This is a document to guide you for the process of data cleaning that I presonally prefere. Everyone has their own way to go about data cleaning, but there are some guidelines to follow. 

I use information from:\
1. Broeck _et al._, 2005. Data Cleaning: Detecting, Diagnosing, and Editing Data Abnormalities.\
2. Elgabry, 2019. [The Ultimate Guide to Data Cleaning.](https://towardsdatascience.com/the-ultimate-guide-to-data-cleaning-3969843991d4)\
3. My personal experience

### Have a grip on your dataset 
To get the big picture of the dataset is the extremely important first step when you start to do everthing else. 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
